A reproduction of Newspapers in Times of Low Advertising Revenues

### 2020-12-16 Outputs/Paper/Paper.Rmd
data cleaning and edit of paper
paper update

---
title: 'A reproduction of Newspapers in Times of Low Advertising Revenues'
author: "Kar Hian Ong"
thanks:  "Code and data are available at: https://github.com/karhian/s4-R-5"
date: "15/12/2020"
bibliography: "references.bib"
abstract: | 
  | In a rapid change industry, the newspaper industry constantly change their ways to apeal to the readers. 
  | **Keywords:** Newspapers, Odinary least squares, Advertising, Internet
output:
  bookdown::pdf_document2:
    fig_caption: yes
    includes:  
      in_header: my_header.tex
toc: FALSE
---

@@

# Data 
The replication data is obtain from openicpsr (@citereplication).

>>>>

---
title: 'A reproduction of Newspapers in Times of Low Advertising Revenues'
author: "Kar Hian Ong"
thanks:  "Code and data are available at: https://github.com/karhian/s4-R-5"
date: "15/12/2020"
bibliography: "references.bib"
abstract: | 
  | In a rapid change industry, the newspaper industry constantly change their ways to apeal to the readers. This paper uses observational data to investigate the effects of advertising revenue on french newspapers. This paper has implication for the newspaper industries and how we look into this industries in the future.
  | **Keywords:** Newspapers, Odinary least squares, Advertising, Internet
output:
  bookdown::pdf_document2:
    fig_caption: yes
    includes:  
      in_header: my_header.tex
toc: FALSE
---

@@

# Data 
The replication data is obtain from openicpsr (@citereplication). The author of the paper co

```{r}
newspapers <- read.csv("../Cleaned data/newspaper_clean.csv")
#remove na's from advertising revenue
newspapers <- newspapers[!is.na(newspapers$ra_cst),]
revenue_year <- aggregate(newspapers['ra_cst'], by=newspapers['year'], sum)
revenue_year %>% ggplot() + geom_point(aes(year,ra_cst)) +labs(x = "Year",
       y = "Advertising revenue")

```

The data shows a general increase in advertising revenue from 1960 to 1974.
